\documentclass[12pt]{report}
\usepackage{scrpage2}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{acronym}
\usepackage{multirow}
\usepackage{parskip}
\usepackage{tikz}
\usetikzlibrary{arrows}
\usepackage{mdframed}
\usepackage{framed}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsmath, amssymb, hyperref}
\graphicspath{{images/}}
\setcounter{secnumdepth}{3}
\setcounter{tocdepth}{4}

\title{
{Development of a Symbolic Model Checker}\\
{\large Institute of Electronic Design and Automation}\\
}
\author{Kasthuri Rengan Narayanan}
\date{Day Month Year}

\begin{document}
\maketitle
\tableofcontents
\chapter*{Abstract}
\input{abstract}
Abstract goes here

\chapter*{List of Acronyms}
\begin{acronym}
\acro{BDD}{Binary Decision Diagram}
\acro{OBDD}{Ordered Binary Decision Diagram}
\acro{ROBDD}{Reduced Ordered Binary Decision Diagram}
\acro{LTL}{Linear Temporal Logic}
\acro{CTL}{Computational Tree Logic}
\acro{SAT}{Satisfiability}
\acro{CNF}{Conjunctive Normal Form}
\acro{DNF}{Disjunctive Normal Form}
\acro{POS}{Product of Sums}
\acro{SOP}{Sum Of Products}
\end{acronym}
\listoffigures
\listoftables
\chapter{Introduction}
\input{chapters/introduction/introduction}

\chapter{Model Checking}
\input{chapters/symbolic_model_checking/symbolic_model_checking}

\chapter{Partitioned Transition Relation}
\input{chapters/partitioned_transition_relation}

\chapter{Cone Of Influence Reduction}
\input{chapters/cone_of_influence_reduction}

\chapter{SAT Solver}
\input{chapters/SAT_solver}


\begin{thebibliography}{99}
\bibitem{Alok 2010} Alok Sanghavi.\textit{What is formal verification?}.21 May 2010: EE Times\_Asia.
\bibitem{Clarke 2008} Edmund M Clarke.\textit{The Birth of Model checking}.25 years of model checking,2008.
\bibitem{McMillan 1993} Kenneth L McMillan.\textit{Symbolic Model Checking: An approach to the State Explosion Problem}.kluwer Academic Publishers,1993.
\bibitem{Burch 1990} J.R. Burch, E.M. Clarke, K.L. McMillan,D.L. Dill and J. Hwang. \textit{Symbolic Model Checking:10\textsuperscript{20} states and beyond}.In proc. 5th Ann.Symp. on Logic in Computer Science. IEEE comp.Soc.Press, June 1990.
\bibitem{Bryant 1986} Randal E Bryant.\textit{Graph-Based Algorithms for Boolean Function Manipulation}.IEEE Transactions on Computers C-35-8:677-691, August 1986.
\bibitem{Lee 1959} C.Y.Lee.\textit{Binary decision programs}.Bell System Technical Journal.38(4):985-999, July 1959.
\bibitem{Bryant 1992} Randal E Bryant.\textit{Symbolic Boolean Manipulation with Ordered Binary Decision Diagrams}.ACM Computing Surveys,1992.
\bibitem{Clarke 1999}Edmund M. Clarke,Orna Grumberg, Doron A. Peled.\textit{Model Checking}.ISBN 0-262-03270-8,1999.
\bibitem{Baier 2008} Christel Baier, Joost-Pieter Katoen.\textit{Principles of model checking}.ISBN 978-0-262-02649-9,2008.
\end{thebibliography}

\end{document}